A GPU Implementation of Capon for an Active Sonar System

### 2012-05-07 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:07	09:46:53	(Mon 7.May)

Figure \ref{holmengraa} demonstrates the potential of the Capon beamformer.

@@

Benchmarks\\
The test system was a quad-core Intel Xeon E5620, 64Gb of \gls{RAM}, and an nVidia Quadro 6000 card. This is a \gls{GPU} with 448 \gls{CUDA} cores and 6Gb of onboard \gls{RAM}, capable of roughly 1Tflops.

>>>>

The Holmengraa demonstrates the Capon beamformer's ability to suppress interference and achieve better detail resolution. Compared the \gls{DAS} beamformer, the ship edges come out as sharper, and the shadows are less noisy. \todo{DAS faster, get it in somehow..}

@@

The Capon parameters influence the complexity of the algorithm. Runtime scale proportionally with the number of image pixels, $M$\todo{prolly not accurate} and $N_\text{avg}$, but not with $L$. To

Figure \ref{benchmarks}. Here the number of channels was set to $M=32$, and

test system was a quad-core Intel Xeon E5620, 64Gb of \gls{RAM}, and an nVidia Quadro 6000 card. This is a \gls{GPU} with 448 \gls{CUDA} cores and 6Gb of onboard \gls{RAM}, capable of roughly 1Tflops.
